An efficient acyclic contact planner for legged robots

### 2017-01-19 body/results.tex
complete paper

\begin{table*}
\centering
\begin{tabular}{ c | c | c | c | c }
 Scenario & Method  & Guide Path & Contact sequence & Interpolation \\
 \hline
   \multirow{3}{*}{Stair 20 cm} & \citeauthor{Hauser06usingmotion} &  \multicolumn{3}{c}{\cellcolor{blue!25}5.42 min}  \\
							 & \textbf{Ours} + \citeauthor{Carpentier2016}  & \textbf{5 ms} & $\mathbf{<}$ \textbf{18 ms} & $ <$ 2s \\
							 & \citeauthor{Mordatch:2012:DCB:2185520.2185539} &  \multicolumn{3}{c}{\cellcolor{blue!25}2 to 10 min} \\
 \hline
   \multirow{3}{*}{Stair 30 cm} & \citeauthor{Hauser06usingmotion} &  \multicolumn{3}{c}{\cellcolor{blue!25}4.08 min}  \\
							 & \textbf{Ours}  & \textbf{5 ms} & $\mathbf{<}$ \textbf{18 ms} & X \\
							 & \citeauthor{Mordatch:2012:DCB:2185520.2185539} &  \multicolumn{3}{c}{\cellcolor{blue!25}2 to 10 min} \\
 \hline
   \multirow{3}{*}{Stair 40 cm} & \citeauthor{Hauser06usingmotion} &  \multicolumn{3}{c}{\cellcolor{blue!25}10.08 min}  \\
							 & \textbf{Ours}  & \textbf{5 s} & \textbf{3 s} & X \\
							 & \citeauthor{Mordatch:2012:DCB:2185520.2185539} &  \multicolumn{3}{c}{\cellcolor{blue!25}2 to 10 min} \\
 %~ \hline
   %~ \multirow{2}{*}{Table (car) egress} & \citeauthor{Bouyarmane2009, DBLP:conf/iser/EscandeKMG08} & 10 min & \multicolumn{2}{c}{\cellcolor{blue!25}3.5 hours}  \\
							 %~ & \textbf{Ours}  & \textbf{529 ms} & \textbf{$<$ 22 s} & X \\
 \end{tabular}
\caption{Comparison between the computation times obtained by our method and previous ones, for each phase of the planning. Blue cells indicate merged times (because no
precise time information is available). The X symbol indicates scenarios where we did not address the interpolation of the contact sequence.}
\label{tab:compprev}
\quad
\end{table*}

\subsection{Validation of the contact plans, and comparison with previous work} \label{sec:compa}
To validate our plans, we had to implement our own interpolation method to address $\mathcal{P}_3$.
We refer the reader to \citep{Carpentier2016} for the implementation details of our method. 
This motion is in turn validated in our dynamic simulator~\citep{DelPrete2015b}. The stair climbing scenario was validated on the real HRP-2 robot \citep{Carpentier2016}.
The obtained motions are available in the video.

Few contributions provided computation times on the complete problem, necessary to provide comparison between our approaches. 
Furthermore, $\mathcal{P}_3$ is an open problem in the presence of obstacles. For instance in \cite{DBLP:conf/iser/EscandeKMG08}, the end-effector trajectories are computed automatically with splines, but are manually corrected if they enter in collision. In \citep{Mordatch:2012:DCB:2185520.2185539}, internal joint collisions can occur in the resulting motion.
Recent methods suffer from similar issues \citep{Carpentier2016}.
The only valid scenarios addressed completely and automatically in previous works are thus the stair climbing scenarios with HRP-2 
To compare our approach with previous contributions, we considered those that addressed the complete problem, and selected scenarios similar to ours, thus focusing on the HRP-2 robot.

Table~\ref{tab:compprev} presents the results we obtained

Nonetheless, we indicate in Table~\ref{tab:compprev} what is actually computed by each method and in how much time.
We compare motions obtained in previous works with HRP-2 (or a humanoid avatar) with ours.
The two scenarios we selected consist in:  climbing one step, of height 20, 30 or 40 centimeters; 
getting out of a table, that we consider of a complexity similar to the car egress scenario (or inferior since the feet locations remain on the ground in the former case).
For scenarios that apply, we also indicate the interpolation time that we obtained by feeding the plan to our interpolation method presented in \cite{Carpentier2016}.

Despite the difficulty of comparing the methods, we believe the results presented in Table~\ref{tab:compprev} indicate that our planner holds the promise of planning complete trajectories significantly faster than previous works.

>>>>

\begin{table*}
\centering
\begin{tabular}{ c | c | c }
 Scenario & Method  & Complete computation time \\
 \hline
   \multirow{3}{*}{Stair 20 cm} & \citeauthor{Hauser06usingmotion} &  5.42 min  \\							 
							  & \citeauthor{Mordatch:2012:DCB:2185520.2185539} & 2 to 10 min \\
							 & \textbf{Ours} + \citeauthor{Carpentier2016}  & \textbf{$ <$ 2s} \\
 \hline
   \multirow{3}{*}{Stair 30 cm} & \citeauthor{Hauser06usingmotion} &  4.08 min  \\
							 & \citeauthor{Mordatch:2012:DCB:2185520.2185539} & 2 to 10 min \\
							 & \textbf{Ours}  & \textbf{$ <$ 2s}   \\
 \hline
   \multirow{3}{*}{Stair 40 cm} & \citeauthor{Hauser06usingmotion} &  10.08 min  \\
							 & \citeauthor{Mordatch:2012:DCB:2185520.2185539} & 2 to 10 min \\
							 & \textbf{Ours}   & \textbf{$ <$ 5s}   \\
 \hline
   \multirow{2}{*}{Table (car) egress} & \citeauthor{Bouyarmane2009, DBLP:conf/iser/EscandeKMG08} & 3.5 hours  \\
							 & \textbf{Ours}  & \textbf{$<$ 60 s} \\

 \end{tabular}
\caption{Comparison between the computation times obtained by our method and previous ones for addressing the whole problem.}
\label{tab:compprev}
\quad
\end{table*}

\subsection{Validation of the contact plans, and comparison with previous work} \label{sec:compa}
To validate our plans, we either use the framework proposed by \citeauthor{Carpentier2016} or our own implementation of a $\mathcal{P}_3$ solver, detailed in Appendix~\ref{app:optim}.
The obtained motions are available in the video.

Few contributions provided computation times on the complete problem, necessary to provide comparison between our approaches. 
Furthermore, $\mathcal{P}_3$ remains an open problem in the presence of obstacles. The only valid scenarios addressed completely in previous works are thus the stair climbing scenarios of different heights proposed by \citeauthor{Hauser06usingmotion}, and the table egress scenario by ~\citeauthor{DBLP:conf/iser/EscandeKMG08}, which we consider to be of similar complexity with respect to the car egress scenario (we did not consider the stairs in the scene). Both scenarios use HRP-2.

Table~\ref{tab:compprev} presents the computation times we obtained for these scenarios, clearly demonstrating that our approach is order of magnitude faster that previous works.
